This work would not have been completed (or at least would not have been nearly as fun to complete) without the fantastic people around me. First and foremost, a great deal of thanks goes to my supervisory team: Tony Belpaeme, Paul Baxter and Angelo Cangelosi. To Angelo, for creating a vibrant group in Plymouth with whom I have shared the last 4 years. To Paul, for your unparalleled support and far too many other things to list, but dark corners and a passion for linguistic obfuscation are a highlight. And to Tony, for so many life changing opportunities, your wit and ineluctable wisdom.

Thank you to all of the ABC group in Plymouth past and present, of whom there are too many to name without forgetting someone, so I won't even try! In particular, thank you to those who have shared an office with me and made the arduous commute worth it: Paul Baxter, Robin Read, Joachim de Greeff, Emily Ashurst, Emmanuel Senft, S\'{e}verin Lemaignan, Fotios Papadopoulos, Bahar Irfan, and Thomas Colin.

The international HRI community has of course shaped my work in many ways. Thank you to anyone who I have discussed my work or ideas with at conferences, workshops, project meetings, summer schools, and so on. I have learnt so much not only academically, but about different places and cultures, which has been an indescribably positive and transformative experience. The wonderful people in the EU ALIZ-E, L2TOR and DREAM projects: you have been a pleasure to collaborate with and I look forward to the remaining time we shall have together in DREAM and L2TOR.

The support of my family has been unwavering, as always. I guess I should thank my dad specifically for finding the advert for the PhD studentship and suggesting that I might like to chance an application to do robotics despite not knowing anything about robots. Somehow that didn't seem to matter.

\vspace{4em}

\textit{Dedicated to the memory of R.A.D. Kennedy.}
%\textit{Dedicated to the memory of Richard Alexander Dunseath Kennedy.}

\vspace{0.7em}
\textit{I know how proud you were when I started this journey; I wish you could have seen the end.}